%alg\documentclass[12pt,a4paper]{amsart}
\documentclass[10pt,a4paper]{article}
%\ifx\pdfpageheight\undefined\PassOptionsToPackage{dvips}{graphicx}\else%
%\PassOptionsToPackage{pdftex}{graphicx}
%\PassOptionsToPackage{pdftex}{color}
%\fi

%\usepackage{diagrams}

\usepackage{color}
\newcommand\coloremph[2][red]{\textcolor{#1}{\emph{#2}}}

\newcommand\greenemph[2][green]{\textcolor{#1}{\emph{#2}}}
\newcommand{\EMP}[1]{\emph{\textcolor{red}{#1}}}

%\usepackage[all]{xy}
\usepackage{url}
\usepackage{verbatim}
\usepackage{latexsym}
\usepackage{amssymb,amstext,amsmath,amsthm}
\usepackage{epsf}
\usepackage{epsfig}
% \usepackage{isolatin1}
\usepackage{a4wide}
\usepackage{verbatim}
\usepackage{proof}
\usepackage{latexsym}
%\usepackage{mytheorems}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[section]


\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}


%%%%%%%%%
\def\oge{\leavevmode\raise
.3ex\hbox{$\scriptscriptstyle\langle\!\langle\,$}}
\def\feg{\leavevmode\raise
.3ex\hbox{$\scriptscriptstyle\,\rangle\!\rangle$}}

%%%%%%%%%


\newcommand\myfrac[2]{
 \begin{array}{c}
 #1 \\
 \hline \hline 
 #2
\end{array}}

\newcommand\HH{\mathrm{H}}
\newcommand\cHH{\check{\mathrm{H}}}
\newcommand{\nats}{\mathbb{N}}
\newcommand{\ints}{\mathbb{Z}}

\newcommand{\ODisc}{\mathsf{ODisc}}
\newcommand{\Stone}{\mathsf{Stone}}
\newcommand{\Boole}{\mathsf{Boole}}
\newcommand{\CHaus}{\mathsf{CHaus}}
\newcommand{\Open}{\mathsf{Open}}
\newcommand{\refl}{\mathsf{refl}}
\newcommand{\Noo}{\nats_{\infty}}
\newcommand{\Ab}{\mathsf{AbGrp}}
\newcommand{\ras}{\twoheadrightarrow}
\newcommand\norm[1]{\left\lVert #1 \right\rVert}



\begin{document}

\title{A characterisation of Stone spaces}

\author{}
\date{}
\maketitle

%\rightfooter{}

\section*{Introduction}

We show that if $X:\CHaus$ then $X$ is Stone iff $X$ is totally disconnected, i.e. the intersection of
decidable subsets containing a given element $x:X$ is the singleton $\{x\}$.

\section{Decidable subsets}

\begin{lemma}\label{stcomp}
  If $S:\Stone$ and $U$ an open subset of $S$ then $\forall_{x:S}U(x)$ is an open proposition.
\end{lemma}

\begin{proof}
  By local choice, we can assume that $U$ is a countable union of $e_n$ decidable subsets of $S$.
  The proposition $\forall_{x:S}U(x)$ is then $\exists_m e_0\vee\dots\vee e_m = 1$ in $2^S$, which is
  an open proposition by countable choice.
\end{proof}


\begin{proposition}\label{chb}
  If $X:\CHaus$ then $2^X:\Boole$.
\end{proposition}

\begin{proof}
  We have $S:\Stone$ and a surjection $p:S\rightarrow X$. We can then see $2^X$ as an open subalgebra
  of $2^S:\Boole$ by the condition $\forall_{y:e}\forall_{z:1-e}p(y)\neq p(z)$, which is open by
  Lemma \ref{stcomp}.
\end{proof}

\begin{corollary}\label{count}
  If $X:\CHaus$ there is a countable enumeration of all elements of $2^X$.
\end{corollary}

\section{Connected component}

Let $X$ be in $\CHaus$. For $x$ in $X$ we let $Q_x$ be the countable intersectionthen from
(using Corollary \ref{count}) of all decidable subsets of $X$ containing $x$. This
is a closed subset of $X$.

\begin{lemma}\label{sep}
  If $Q_x\subseteq U$ with $U$ open, then there exists $e$ decidable subset of $X$
  such that $x\epsilon e$ and $e\subseteq U$.
\end{lemma}

\begin{proof}
  This follows from compactness of $X$: we have $\cap_{x\epsilon e_n}e_n\cap (X-U) = \emptyset$
  and hence then exists $e$ in $2^X$ such that $x\epsilon e$ and $e\cap (X-U) = \emptyset$.
\end{proof}

\begin{lemma}\label{conn}
  $Q_x$ is the connected component of $x$.
\end{lemma}

\begin{proof}
  It is enough to show that $Q_x$ is connected. Let $Q_x = A\cup B$ with $A$ and $B$ closed/open
  disjoint subsets of $Q_x$. Then $A$ and $B$ are disjoint closed subsets of $X$ and hence, since $X:\CHaus$,
  there exists disjoint open $U$ and $V$ such that $A\subseteq U$ and $B\subseteq V$.
  We have $x$ in $A$ or $x$ in $B$. Let say that $x$ is in $A$ and we show that $B = \emptyset$.

  By Lemma \ref{sep}, we have $e$ in $2^X$ such that $x\epsilon e$ and $e\subseteq U\cup V$.
  Then $e'= e\cap U = e\cap (X-V)$ is both closed and open, hence decidable, and $e'\cap B = \emptyset$
  and $B\subseteq Q_x\subseteq e'$, hence $B = \emptyset$.
\end{proof}

\begin{theorem}\label{char}
  We have $\forall_x Q_x = \{x\}$ iff $X:\Stone$.
\end{theorem}

\begin{proof}
  The map $X\rightarrow Hom(2^X,2)$ is always surjective by compactness.
  If $\forall_x Q_x = \{x\}$ this map is also injective, and the result follows then from
  Proposition \ref{chb}.
\end{proof}

The following application was noticed by Martin Escardo. We know by local choice
that if $S:\Stone$ and $F:S\rightarrow\Stone$ then $\Sigma_SF:\CHaus$.
We use Theorem \ref{char} to refine this to $\Sigma_SF:\Stone$.

\begin{lemma}
  If $Q$ is connected and $S:\Stone$ and $f:Q\rightarrow S$ then $f$ is constant.
\end{lemma}

\begin{proof}
  For $x$ and $y$ in $Q$ we show $f(x)=f(y)$. Since $f(x) = f(y)$ is a closed proposition
  we show that $f(x)\neq f(y)$ is contradictory. If $f(x)\neq f(y)$ there exists $e$ decidable
  subset of $S$ such that $f(x)$ in $e$ and $f(y)$ in $S-e$. But then $f^{-1}(e)$ is a decidable
  subset of $Q$ containing $x$ and not $y$, and this contradicts $Q$ being connected.
\end{proof}

\begin{corollary}
  Stone spaces are closed by dependent sum types.
\end{corollary}

\begin{proof}
  We assume $S:\Stone$ and $F:S\rightarrow \Stone$. We know that $X = \Sigma_SF$ is in $\CHaus$
  and we show $X:\Stone$ using Theorem \ref{char}. We take $a:S$ and $b:F(a)$ and show that the
  connected component $Q_x$ of $x = (a,b)$ is a singleton. Using the previous Lemma for
  $\pi_1:X\rightarrow S$ we have $Q_x$ subset of $\{a\}\times F(a)$. Since $F(a)$ is Stone this
  is a singleton.
\end{proof}


\end{document}     
                                                                                  
