Cohomology has the universal property of being a \notion{universal $\partial$-functor}.
In this section, we will construct a tool for proving this in some particular situations,
both for the cohomology defined using Eilenberg-MacLane spaces and \v{C}ech cohomology.

The following definition, from (\cite[2.1]{tohoku-translation}) and originally from (\cite{tohoku1957}), is specialized to our needs.
Grothendieck makes a definition for additive functors from an abelian category to a preadditive category.
We will only need the theory for functors from certain subcategories of dependent $R$-modules over a fixed type to abelian groups.
Also, some arguments are a lot more convenient when we can use elements of modules instead of abstract categorical language.
Therefore, we will state our definitions and results only for this particular situation.

\emph{Let $R$ be a fixed commutative ring and $\mathcal A$ be a subcategory of the category of dependent $R$-modules over a fixed type $X$, which is closed under finite direct sums.}

\begin{definition}
  An \notion{($l$-truncated) $\partial$-functor} is a collection of additve\footnote{
    The zero object and binary direct sums are preserved.
  }
  functors
  $T^i:\mathcal A\to \AbGroup$, where $0\leq i < l$ with $l\in\N\cup\{\infty\}$,
  together with a collection of connecting morphisms $\partial_{S,i}$ for any short exact sequence $S$ and $0\leq i\le l$, subject to the following conditions:
  \begin{enumerate}[(a)]
  \item Let $\mathcal{S}$ be a short exact sequence
    \[ 0\to A'\to A\to A''\to 0\]
    in $\mathcal A$. Applying the $T^i$ yields a complex, together with connecting morphisms $(\partial_{\mathcal{S},i})_{0\leq i<l-1}$:
    \begin{center}
      \begin{tikzcd}
        0\ar[r] & T^0(A')\ar[r] & T^0(A)\ar[r]  & T^0(A'')\ar[r,"\partial_{\mathcal{S},0}"]  & T^1(A')\ar[r]  & T^1(A)\ar[r]  & \dots
      \end{tikzcd}
    \end{center}
  \item For any homomorphism to a second short exact sequence
    \[ 0\to B'\to B\to B''\to 0\]
    and any $i<l-1$ the corresponding square commutes:
    \begin{center}
      \begin{tikzcd}
        T^i(A'')\ar[r,"\partial"]\ar[d] & T^{i+1}(A')\ar[d] \\
        T^i(B'')\ar[r,"\partial"] & T^{i+1}(B') \\
      \end{tikzcd}
    \end{center}
  \end{enumerate}
\end{definition}

\begin{definition}
  Let $l,k:\N$.
  The $l$-th \notion{truncation} of a $(l+k)$-truncated $\partial$-functor $T$
  is just the restriction of $(T^i)_{i<l+k}$ to $(T^i)_{i<l}$, together with a restriction of the $\partial$-maps
  and we denote the $l$-th truncation with \notion{$T^{\leq l}$}.
\end{definition}

\begin{definition}
  Let $T$ and $T'$ be $\partial$-functors defined for the same indices.
  
  A \notion{morphism of $\partial$-functors} $f:T\to T'$ is given by a natural transformation $f^i:T^i\to T'^i$ for each valid $i$,
  such that for any short exact sequence
  \[ 0\to A'\to A\to A''\to 0\]
  the following square commutes:
  \begin{center}
    \begin{tikzcd}
      T^i(A'')\ar[r,"\partial"]\ar[d,"f^i_{A''}"] & T^{i+1}(A')\ar[d,"f^{i+1}_{A'}"] \\
      T'^i(A'')\ar[r,"\partial"] & T'^{i+1}(A') 
    \end{tikzcd}
  \end{center}
\end{definition}

\begin{definition}
  A $\partial$-functor $T$ is called \notion{exact},
  if all values are exact complexes.
\end{definition}

\begin{definition}
  A $\partial$-functor $T$ is called \notion{universal}, if for any $T'$, defined for the same indices,
  any natural transformation $f^0:T^0\to T'^0$ extends uniquely to a morphism of $\partial$-functors $f:T\to T'$.
\end{definition}

To prove that some $\partial$-functor has this universal property,
we will \emph{extend} morphisms of $\partial$-functors, level by level.
By observing the diagram in the proof of the lemma below,
one can see that this is possible using exact sequences with the property,
that some particular element is zero in their middle term.
This property will appear often enough to deserve a name:

\begin{definition}
  Let $T$ be a $\partial$-functor, $i$ a valid index, $A:\mathcal A$ and $\chi:T^i(A)$.
  We say that a short exact sequence $\mathcal{S}=A\to R\to S$ \notion{resolves} $\chi$,
  if $\chi$ is mapped to zero in $T^i(R)$.
\end{definition}

In the classical approach with injective resolutions,
for a fixed $A:\mathcal A$ all elements of $T^i(A)$ for all $i>0$ would be resolved.
For our examples, where we can resolve elements of $H^i(X,A)$,
we will only be able to \emph{merely} resolve one $\chi:H^i(X,A)$ at a time.
So resolving all elements at once with the same construction, would require some form of choice.

We will now show,
how a short exact sequence resolving an element might be of use to extend morphisms of $\partial$-functors.

\begin{lemma}
  \label{lem:extend-map}
  Let $l\geq i>0$ and $T$ be an exact, $l$-truncated $\partial$-functor, $\mathcal{S}=A\to R_\chi\to S_\chi$ a short exact sequence in $\mathcal A$
  and $\chi:T^i(A)$
  \begin{center}
    \begin{tikzcd}
      A\ar[r,"r_\chi"] & R_\chi\ar[r,"s_\chi"] & S_\chi
    \end{tikzcd}
  \end{center}
  that resolves $\chi$, i.e. such that $T^i(r_\chi)(\chi)=0$.
  For an $l$-truncated $\partial$-functor $T'$
  and any morphism of $(i-1)$-truncated $\partial$-functors $f:T^{\leq (i-1)}\to T'^{\leq (i-1)}$,
  there is a unique\index{$\mathrm{ext}(f,\chi,\mathcal{S})$}
  \[\mathrm{ext}(f,\chi,\mathcal{S}) : T'^i(A)\]
  such that for any $x:T^{i-1}(S_\chi)$ with $\partial_{T,\mathcal{S},i-1}(x)=|\chi|$ we have $\partial_{T,S,i-1}(f^{i-1}(x))=\mathrm{ext}(f,\chi,\mathcal{S})$.
\end{lemma}

\begin{proof}
  The following diagram commutes:
  \begin{center}
    \begin{tikzcd}
      T^{i-1}(A)\ar[r]\ar[d,"f^{i-1}"]  & T^{i-1}(R_\chi)\ar[r]\ar[d,"f^{i-1}"]  & T^{i-1}(S_\chi)\ar[r,"\partial"]\ar[d,"f^{i-1}"] & T^i(A)\ar[r,"r_\chi^\ast"] & T^i(R_\chi)\dots \\
      T'^{i-1}(A)\ar[r]  & T'^{i-1}(R_\chi)\ar[r,"s_\chi^\ast"]  & T'^{i-1}(S_\chi)\ar[r,"\partial"] & T'^i(A)\ar[r] & T'^i(R_\chi)\dots 
    \end{tikzcd}
  \end{center}
  The upper row is exact and the lower row is a complex.

  Let $E(\chi,\mathcal{S})$ be the type of all possible values of $f^i$ in $T'^i(A)$,
  with which the dependent sum over all $y:T'^i(A)$ such that there merely is $x:T^{i-1}(S_\chi)$ with $\partial(x)=|\chi|$
  and $\partial(f^{i-1}(x))=y$.
  Then $E(\chi,\mathcal{S})$ is inhabited, since $r_\chi(|\chi|)=0$ and by exactness, there has to be a mere preimage under $\partial$.
  So we need to show, that $E(\chi,\mathcal{S})$ is a proposition.
  
  Let $x:T^{i-1}(S_\chi)$ such that $\partial(x)=|\chi|$.
  Then any other element with this property will be of the form $x+k$, with $k$ in the kernel of $\partial$.
  Any $k$ like that, has a mere preimage $k':T^{i-1}(R_\chi)$ and since the lower row is a complex, we have $\partial(s_\chi^\ast(f^{i-1}(k')))=0$.
  
  So for any extension $y:T'^{i}(A)$ we have
  \begin{align*}
    y &= \partial(f^{i-1}(x+k)) \\
      &= \partial(f^{i-1}(x))+\partial(f^{i-1}(k)) \\
      &= \partial(f^{i-1}(x))+\partial(s_\chi^\ast(f^{i-1}(k'))) \\
      &= \partial(f^{i-1}(x))
  \end{align*}
  This means we can define $\mathrm{ext}(f,\chi,\mathcal{S})$ to be the unique element of $E(\chi,\mathcal{S})$.
\end{proof}

While this shows, that existence of these special short exact sequences
is enough to extend a \emph{map} from one truncation level to the next,
it is not clear, that an extension constructed in this way,
is actually a morphism of truncated $\partial$-functors.

It is also unclear, if the construction even yields a well-defined map,
independent of the short exact sequence we chose in the construction.
A solution to these problems is essentially given by
requiring some ``functoriality'' of the short exact sequences we will use (\cref{local-resolution}) and
the following naturality result:

\begin{lemma}
  \label{lem:extension-welldefined}
  Let $T$ be an exact $\partial$-functor.
  Let $\chi:T^i(A)$ and
  \begin{center}
    \begin{tikzcd}
      A\ar[r,"r_\chi"]\ar[d,"\varphi"] & R_{\chi}\ar[r]\ar[d,"\varphi_R"] & S_{\chi}\ar[d,"\varphi_S"] \\
      A'\ar[r] & R_{\varphi(\chi)}\ar[r] & S_{\varphi(\chi)}
    \end{tikzcd}
  \end{center}
  be a morphism of short exact sequences ${\mathcal S}_\chi$ and $\mathcal{S}_{\varphi(\chi)}$ in $\mathcal A$,
  where $T^i(r_\chi)(\chi)=0$.
  Then, for the construction from \cref{lem:extend-map}, we have the following commutativity:
  \[ T^i(\varphi)(\mathrm{ext}(f,\chi,{\mathcal S}_\chi)) = \mathrm{ext}(f,\varphi(\chi),\mathcal{S}_{\varphi(\chi)}) \]
\end{lemma}

\begin{proof}[of \cref{lem:extension-welldefined}]
  Let $T'$ be another $\partial$-functor and $f:T^{\leq i-1}\to T'^{\leq i-1}$.
  Apply the $\partial$-Functors $T$ and $T'$ to the morphism of short exact sequences,
  to get the following diagram:
  \begin{center}
    \begin{tikzcd}
      T^{i-1}(R_\chi)\ar[r]\ar[dr]\ar[dd,"f^{i-1}"] &
      T^{i-1}(S_\chi)\ar[r]\ar[dr]\ar[dd, shift right=1ex, near start, "f^{i-1}"] &
      T^i(A)\ar[r]\ar[dr,"\varphi^\ast"] & T^i(R_\chi)\dots\ar[dr] & \\
      & T^{i-1}(R_{\varphi(\chi)})\ar[r]\ar[dd,"f^{i-1}",crossing over,near start] &
      T^{i-1}(S_{\varphi(\chi)})\ar[r]\ar[dd,crossing over, near start, "f^{i-1}"] & T^i(A')\ar[r] & T^i(R_{\varphi(\chi)})\dots \\
      T'^{i-1}(R_\chi)\ar[r] & T'^{i-1}(S_\chi)\ar[r]\ar[dr] & T'^i(A)\ar[r]\ar[dr,"T'^i(\varphi)"] & T'^i(R_\chi)\dots\ar[dr] & \\
      & T'^{i-1}(R_{\varphi(\chi)})\ar[r] & T'^{i-1}(S_{\varphi(\chi)})\ar[r] & T'^i(A')\ar[r] & T'^i(R_{\varphi(\chi)})\dots \\
      
      & a\ar[mapsto,r]\ar[dd,mapsto]\ar[rd,mapsto] & \chi\ar[r,mapsto]\ar[rd,mapsto] & 0\ar[rd,mapsto] & \\
      & & a'\ar[mapsto,r]\ar[dd,mapsto] & {\varphi(\chi)}\ar[r,mapsto] & 0 \\
      & b\ar[rd,mapsto]\ar[r,mapsto]& \mathrm{ext}(\chi,R_\chi)\ar[rd,mapsto] & & \\
      & & b'\ar[r,mapsto] & ? & 
    \end{tikzcd}
  \end{center}
  From exactness of the upper sequence, we get that there is a preimage $a$ of $\chi$.
  Let $a'$ denote the image of $a$ in $T^{i-1}(S_{\varphi(\chi)})$,
  then $a'$ will be a preimage of ${\varphi(\chi)}$ in the parallel sequence by commutativity.
  That means, that $b'$, the image of $a'$ in the lower sequence,
  will be mapped to $ \mathrm{ext}(f,\varphi(\chi),\mathcal{S}_{\varphi(\chi)})$,
  but by commutativity, $\mathrm{ext}(f,\chi,\mathcal{S}_\chi)$ will be mapped to the same thing by $T^i(\varphi)$.
  So:
  \[ T^i(\varphi)(\mathrm{ext}(f,\chi,\mathcal{S}_\chi))=\mathrm{ext}(f,\varphi(\chi),\mathcal{S}_{\varphi(\chi)})\]  
\end{proof}

We summarize the exact condition we found useful to prove universality of $\partial$-functors,
together with the existence of enough ``good'' short exact sequences in the following definition.

\rednote{The following is about to be replaced with a more specialized but easier notion, focusing on trivializing covers instead of resolving sequences.
 One good thing about asking for trivializing covers should be that the big diagram below will only appear in one proof instead of a couple of places.}

\begin{definition}
  \label{local-resolution}
  Let $T$ be a $\partial$-functor.
  We say that $\mathcal A$ \notion{has local resolutions for $T$}, if
  \begin{enumerate}[(i)]
  \item For any $i>0$, $A:\mathcal A$ and $\chi:T^i(A)$ there merely is a short exact sequence:
    \[
      \begin{tikzcd}
        0\ar[r] & A\ar[r,"m_\chi"] & M_\chi\ar[r] & C_\chi\ar[r] & 0
      \end{tikzcd}
    \]
    resolving $\chi$, i.e. such that $T^i(m_\chi)(\chi)=0$.
  \item For any short exact sequence $\mathcal{S}=A\to R\to S$ resolving $\chi$
    and any morphism $\varphi:A\to B$,
    there is a zig--zag of short exact sequences resolving $\chi$ or, respectively $\varphi(\chi)$,
    of the following shape:
    \begin{center}
      \begin{tikzcd}
        A\ar[r]\ar[d,equal] & R\ar[r]\ar[d] & S\ar[d] \\
        A\ar[r] & R_1\ar[r] & S_1 \\
        \vdots\ar[u,equal] & \vdots\ar[u] & \vdots\ar[u] \\
        A\ar[r]\ar[d,"\varphi"] & R_l\ar[r]\ar[d] & S_l\ar[d] \\
        B\ar[r] & M_{\varphi,\mathcal{S}}\ar[r] & C_{\varphi,\mathcal{S}} \\
        B\ar[r,"m_{\varphi(\chi)}"]\ar[u,equal] & M_{\varphi(\chi)}\ar[r]\ar[u] & C_{\varphi(\chi)}\ar[u]
      \end{tikzcd}
    \end{center}
  \end{enumerate}
\end{definition}


The following is provable by a constructive adaption of Prop 2.2.1 in \cite{tohoku-translation}:
\begin{theorem}
  \label{thm:universal}
  Let $X$ be a type.
  An exact $\partial$-functor $(T^i)_{i<l}$ from $\mathcal A$ to $\AbGroup$ is universal,
  if $\mathcal A$ has local resolutions for $T$.
\end{theorem}

\begin{proof}[of \cref{thm:universal}]
  To extend a given morphism $f^0$, 
  we will construct $f^i:T^i\to T'^i$ by induction on $i$ for $0<i<l$.
  So let $T'$ be a $\partial$-functor and assume, we already have a morphism for $i-1$ and lower indices.
  We start by constructing a group homomorphism $f^i:T^i(A)\to T'^i(A)$ for arbitrary $A:\mathcal A$.

  By \cref{lem:extend-map},
  we merely get $f^{i}(\chi)\colonequiv \mathrm{ext}(f,\chi,\mathcal{S}_\chi)$,
  for each $\chi:T^i(A)$ and their merely given local resolutions $\mathcal{S}_\chi$.
  To see that this yields an actual map, we have to check that the
  values $\mathrm{ext}(f,\chi,\mathcal{S}_\chi)$ are independent of the short exact sequence $\mathcal{S}_\chi$.
  For any other short exact sequence $\mathcal{S}'=A\to R_\chi\to S_\chi$
  that resolves $\chi$, we get a zig-zag by our requirement on local resolutions:
  \begin{center}
    \begin{tikzcd}
      A\ar[r]\ar[d,equal] & R_\chi\ar[r]\ar[d] & S_\chi\ar[d] \\
      A\ar[r] & R_1\ar[r] & S_1 \\
      \vdots\ar[u,equal] & \vdots\ar[u] & \vdots\ar[u] \\
      A\ar[r]\ar[d,"\id"] & R_l\ar[r]\ar[d] & S_l\ar[d] \\
      A\ar[r] & M_{\id,\mathcal{S}'}\ar[r] & C_{\id,\mathcal{S}'} \\
      A\ar[r,"m_{\chi}"]\ar[u,equal] & M_{\chi}\ar[r]\ar[u] & C_{\chi}\ar[u]
    \end{tikzcd}
  \end{center}
  Applying \cref{lem:extension-welldefined} to any of these morphisms $\mathcal{S}\to\mathcal{S}'$ of exact sequences
  gives us:
  \[ \mathrm{ext}(f,\chi,\mathcal{S}) = T^i(\id)(\mathrm{ext}(f,\chi,\mathcal{S}')) = \mathrm{ext}(f,\chi,\mathcal{S}') \]
  So we have a well-defined map $f^{i}:T^i(A)\to T'^i(A)$.
  We will show that it is a homomorphism of groups.
  First, note that $f^i(0)=0$,
  because $0$ has the identity as a local resolution, i.e. the sequence $0\to A\to A\to 0\to 0$.
  
  Now let $\xi,\chi,\xi+\chi:T^i(A)$.
  We need to show that $f^i(\xi)+f^i(\chi)=f^i(\xi+\chi)$.
  By additivity of the $T^i$,
  we can ``resolve'' these three elements at once, applying our construction to $(\xi,\chi,\xi+\chi):T^i(A\oplus A\oplus A)$.
  Again by \cref{lem:extension-welldefined} using the inclusions $A\to A\oplus A\oplus A$,
  we get $f^i(\xi,\chi,\xi+\chi)=(f^i(\xi),f^i(\chi),f^i(\xi+\chi))$.
  By using \cref{lem:extension-welldefined} on the map $a\colonequiv (x,y,z)\mapsto x+y-z:A\oplus A\oplus A\to A$, we get:
  \begin{align*}
    f^i(\xi)+f^i(\chi)-f^i(\xi+\chi) &=T^i(a)((f^i(\xi),f^i(\chi),f^i(\xi+\chi))) \\
                                     &=f^i(a(\xi,\chi,\xi+\chi)) \\
                                     &=f^i(0) \\
                                     &=0
                                       \rlap{.}
  \end{align*}
  This shows that $f^i$ is as homomorphism.
  
  Let $\mathcal{S}=A\to B\to C$ be an arbitrary exact sequence.
  To see that $f^i$ commutes with the connecting morphism $\partial_{\mathcal{S},i-1}$,
  let $x:T^{i-1}(C)$ and $\chi$ be the image of $x$ in $T^i(A)$.
  By exactness, $\chi$ will be mapped to 0 in $T^i(B)$, so $\mathcal{S}$
  resolves $\chi$ and therefore, the desired commutativity follows from the well-definedness proof for $f^i$.
  
  The only thing left to show
  is that $f^i$ is a natural transformation $T^i\to T'^i$.
  Let $\varphi:A\to B$ and $\chi:T^i(A)$.
  By our definition of local resolutions,
  there is a zig-zag:
  \begin{center}
    \begin{tikzcd}
      A\ar[r]\ar[d,equal] & R_\chi\ar[r]\ar[d] & S_\chi\ar[d] \\
      A\ar[r] & R_1\ar[r] & S_1 \\
      \vdots\ar[u,equal] & \vdots\ar[u] & \vdots\ar[u] \\
      A\ar[r]\ar[d,"\varphi"] & R_l\ar[r]\ar[d] & S_l\ar[d] \\
      B\ar[r] & M_{\varphi,\mathcal{S}'}\ar[r] & C_{\varphi,\mathcal{S}'} \\
      B\ar[r,"m_{\varphi(\chi)}"]\ar[u,equal] & M_{\varphi(\chi)}\ar[r]\ar[u] & C_{\varphi(\chi)}\ar[u]
    \end{tikzcd}
  \end{center}
  and therefore by applying \cref{lem:extension-welldefined} to the but last rectangle:
  \begin{align*}
    T^i(\varphi)(f^i(\chi)) &= T^i(\varphi)(\mathrm{ext}(f,\chi,\mathcal{S}_l)) \\
                            &=\mathrm{ext}(f,\varphi(\chi),\mathcal{M}) \\
                            &=f^i(\varphi(\chi))
                              \rlap{.}
  \end{align*}
\end{proof}
