\subsection{Strange Modules}\label{strange-modules}

\rednote{These are meant to be ideas/WIP that might not appear in a final draft.}

Given a type $U$, one can form the following modules:
\begin{equation}\label{eq:strange-sup}
  \begin{tikzcd}
    0 \ar[r] & K^U \ar[r,hook] & R \ar[rr,"c"] \ar[rd,->>] && R^U \\
             &                  &            & R/K^U \ar[ru]
  \end{tikzcd}
\end{equation}
where $c$ sends $r$ to the constant function with value $r$,
$K^U$ is defined to be the kernel of $c$, and $R/K^U$ is the image of $c$.
Note that $K^U = \sum_{x:R} (U \to (x=0))$.
Since $c$ is a ring homomorphism, $K^U$ is an ideal, and $R/K^U$ is also a ring.
When $U$ is affine, $R^U$ is wqc, and therefore so are $K^U$ and $R/K^U$.
When $U$ is a closed proposition, such as $V(r)$, we know that
$R^U$ is finitely adequate, which implies that $K^U$ and $R/K^U$ are as well.
\rednote{Citation?}

For any $U$, $R^U$ is tangential by \cref{prp:exp-tangential},
and therefore this follows for $K^U$ and $R/K^U$ as well using \cref{prp:lim-col-ext-tangential}.
By the same argument, all three are infinitesimally linear, using \cref{prp:lim-inf-lin,prp:cok-ext-inf-lin}.

We can also form
\begin{equation}\label{eq:strange-sub}
  \begin{tikzcd}
    0 \ar[r] & R_U \ar[r,hook] & R \ar[r,->>] & R/R_U \ar[r] & 0
  \end{tikzcd}
\end{equation}
where $R_U$ is the submodule defined by the predicate sending
$x : R$ to $(x = 0) \lor \propTrunc{U}$.
For this sequence, we may as well assume that $U$ is a proposition.
Again, I think $R_U$ is an ideal and the quotient is a ring.
We show below that $R_U$ and $R/R_U$ are tangential.
\textbf{Are they infinitesimally linear?}

In total, this gives five modules that depend on a type $U$,
three of which are rings.
When $U$ is a proposition, all five are not not finitely adequate, since they
are finitely adequate when $U$ is true or false.
In fact, all five are not not finite free.

There is a relationship between \eqref{eq:strange-sub} for $\lnot U$
(top row in the following diagram)
and \eqref{eq:strange-sup} for $U$ (bottom row):
\begin{equation}\label{eq:strange-compare}
  \begin{tikzcd}
    0 \ar[r] & R_{\lnot U} := \sum_{x : R} (x = 0) \lor \lnot U \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>] \ar[d,equal] & R/R_{\lnot U} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & K^U := \sum_{x : R} (U \to (x = 0)) \ar[r,hook]
    & R \ar[r,->>] & R/K^U \ar[r] & 0
  \end{tikzcd}
\end{equation}
The downwards inclusion on the left is easy to check:  Let $x : R$.  If $x = 0$,
then $x$ is clearly in the submodule $K^U$, and if $\lnot U$, then $R^U = 0$, so $K^U$ is all
of $R$, so $x$ is in $K^U$.
This map is a monomorphism, since it factors one.
The epimorphism on the right follows formally.
Note that the modules on the left have the same non-zero elements, and therefore
in the cokernel $K^U / R_{\lnot U}$ every element is not not zero.
Also note that this cokernel is equivalent to the kernel of the right-hand epimorphism,
by the snake lemma.

Specializing \eqref{eq:strange-sub} to $U = V(r) = \Spec R/(r) = (r = 0)$,
for a chosen $r : R$, gives the top row of this diagram,
which is related to the kernel-image exact sequence coming from the
map $\varphi_r : R \to R$ that multiplies by $r$:
\begin{equation*}
  \begin{tikzcd}
    0 \ar[r] & R_{V(r)} := \sum_{x : R} (x = 0) \lor (r = 0) \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>] \ar[d,equal] & R/R_{V(r)} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & \ker \varphi_r := \sum_{x : R} (xr = 0) \ar[r,hook]
    & R \ar[r,->>] & \im \varphi_r = (r) \ar[r] & 0
  \end{tikzcd}
  \tag{$\ast$}
\end{equation*}
The downwards inclusion on the left is easy to see, and the downwards
epimorphism on the right follows formally.
(This is not a special case of \eqref{eq:strange-compare}.)
Note that $\ker \varphi_r$ is finitely copresented, and so is finitely adequate.
Therefore, $\im \varphi_r$ is finitely adequate as well.

Recall that $D(r) = \lnot V(r) = (r \neq 0) = \inv(r) = \Spec R[1/r]$, so
\eqref{eq:strange-compare} with $U = V(r)$ involves $V(r)$ and $D(r)$:
\begin{equation}\label{eq:compare-Vr}
  \begin{tikzcd}
    0 \ar[r] & R_{D(r)} := \sum_{x : R} (x = 0) \lor (r \neq 0) \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>,"q"] \ar[d,equal] & R/R_{D(r)} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & K^{V(r)} := (r) \ar[r,hook]
    & R \ar[r,->>,"c"] & R^{V(r)} = R/(r) \ar[r] & 0
  \end{tikzcd}
\end{equation}
Here note that $R^{V(r)} = R/(r)$ since $V(r) = \Spec R/(r)$, and so the kernel of $c$ is $(r)$.
Also, the map $c$ is epi in this case, so $R^{V(r)}= R/K^{V(r)}$.
Since $V(r)$ is closed, the modules in the bottom row are finitely adequate.
(This is also easy to see directly in this case, as $R/(r)$ is finitely presented.)

For each $r : R$, $r$ is in the submodule $K^{V(r)} = (r)$.  But the statement that
for each $r$, $r$ is in the submodule $R_{D(r)}$ is equivalent to the statement that
$R$ has decidable equality, which contradicts duality.  \rednote{Is this precisely
written somewhere?}  Therefore, it is not the case that the inclusion map is an
equivalence for every $r : R$.

The map $q$ in the previous diagram has the property that $\lnot (q(r) \neq 0)$.
Indeed, assume that $q(r) \neq 0$.  Then $r \neq 0$, and therefore $R/R_{D(r)} = 0$,
so $q(r) = 0$, a contradiction.
\textbf{Questions:}
Does this mean that $q(r)$ is nilpotent in the ring $R/R_{D(r)}$?
Or does the relationship between not non-zero and nilpotence only work for the ring $R$?
Is $q$ the universal map for which $\lnot (q(r) \neq 0)$?

Next we can consider \eqref{eq:strange-compare} with $U := D(r)$, so
$\lnot U = \lnot (r \neq 0)$.  We get
\begin{equation*}
  \begin{tikzcd}
    0 \ar[r] & R_{\lnot D(r)} := \sum_{x : R} (x = 0) \lor \lnot (r \neq 0) \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>] \ar[d,equal] & R/R_{\lnot D(r)} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & K^{D(r)} = \sum_{x : R} \exists_n (r^n x = 0)  \ar[r,hook]
    & R \ar[r,->>] & R/K^{D(r)} \ar[r] & 0
  \end{tikzcd}
  \tag{$\ast$}
\end{equation*}
where $R/K^{D(r)}$ is the image of $R$ in $R^{D(r)} = R[1/r]$.
The displayed description of $K^{D(r)}$ follows from the construction of $R[1/r]$
using equivalence classes of fractions.  \rednote{Citation?}
The modules in the bottom row are wqc, since $D(r)$ is affine.

Finally, consider \eqref{eq:strange-compare} with $U := \lnot D(r)$, noting that
$\lnot \lnot D(r) = D(r)$ (since $D(r)$ is already a negation).
This gives the first two rows of
\begin{equation*}
  \begin{tikzcd}
    0 \ar[r] & R_{D(r)} := \sum_{x : R} (x = 0) \lor (r \neq 0) \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>,"q"] \ar[d,equal] & R/R_{D(r)} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & K^{\lnot D(r)} \ar[r,hook] \ar[d,hook]
    & R \ar[r,->>,"q'"] \ar[d,equal] & R/K^{\lnot D(r)} \ar[r] \ar[d,->>] & 0 \\
    0 \ar[r] & K^{V(r)} := (r) \ar[r,hook]
    & R \ar[r,->>,"c"] & R^{V(r)} = R/(r) \ar[r] & 0
  \end{tikzcd}
  \tag{$\ast$}
\end{equation*}
The first row is the same as the first row of \eqref{eq:compare-Vr}, and in fact, since we
have a map $V(r) \to \lnot D(r)$, that diagram factors through this one, as shown.

\textbf{It would be nice to understand the middle row better.}
Observe that $\lnot D(r) = \lnot \lnot (r = 0)$ and $(r = 0) = \Spec(R/\langle r \rangle)$ is a closed subtype of $\Spec(R)$, so by Lemma 1.1.2 of Topology of Synthetic Schemes draft we say that $\lnot D(r)$ is the formal neighbourhood of $(r = 0)$.
\rednote{This notion of formal neighbourhood is different than the one presented in Differential Geometry of Synthetic Schemes draft.}
Again, by Lemma 1.1.2, we get that $\lnot D(r) = \bigcup{k : \mathbb{N}}(r^k = 0)$.
\rednote{This description of $\lnot D(r)$ is probably derivable directly from $\lnot D(r)$ being the proposition that $r$ is nilpotent.}
Using continuity of the exponential and duality we can compute $R^{\lnot D(r)} = R^{\bigcup{k : \mathbb{N}}(r^k = 0)} = \lim_k R^{(r^k = 0)} = \lim_k R/\langle r^k \rangle = \widehat{R_r}$.
It follows that $K^{\lnot D(r)} = \bigcap_k \langle r^k \rangle$.
Given some $r : R$ that is either invertible or nilpotent, we can deduce that $R^{\lnot D(r)}$ and $K^{\lnot D(r)}$ are finitely adequate.
The following proposition tells us that we cannot assert that $R^{\lnot D(r)}$ is finitely adequate for all $r : R$.

\begin{proposition}
  It is impossible to prove that for every $r : R$ the module $R^{\lnot D(r)}$ is wqc.
\end{proposition}

\begin{proof}
  Assume that for any $r : R$ we know that $R^{\lnot D(r)}$ is wqc.
  By virtue of duality, the global sections of the bundle ${r \mapsto R^{\lnot D(r)}}$ form the power series module:
  \[
    R[[x]] = \lim_n R[x]/(x^n) = R^{\mathrm{colim}_n \Spec R[x]/(x^n)}= R^{\{r:R | \lnot\lnot(r=0)\}} = \prod_{r : R} R^{\lnot D(r)}\rlap{.}
  \]
  By Lemma 7.1.10 of A Foundation for Synthetic Algebraic Geometry, we can deduce that $R[[x]]$ is wqc, which contradicts Proposition A.0.5 of the same paper.
\end{proof}

Other questions:
Is the map $c : R \to R^{\lnot D(r)}$ epic in this case?
Is $c(r)$ nilpotent?

We can also show similar results for $R/R_{D(r)}$ and $R_{D(r)}$.

% This is almost entirely due to Claude, with a bit of guidance from jdc.
% jdc also edited the writing.
\begin{proposition}\label{prp:quot-RDr-not-wqc}
  It is impossible to prove that for every $r : R$ the module $R/R_{D(r)}$ is weakly
  quasi-coherent.  In particular, it is impossible to prove that for every $r : R$ the
  module $R/R_{D(r)}$ is finitely adequate.
\end{proposition}

\begin{proof}
  The second statement follows from the first, since finitely adequate modules are
  weakly quasi-coherent (\cref{prp:fin-adeq-adeq}).

  For the first, assume that $R/R_{D(r)}$ is weakly quasi-coherent for every $r : R$.
  Fix $r : R$, and recall that $D(r) := (r \neq 0)$ is a proposition and that
  $R_{D(r)} = \sum_{x : R} (x = 0) \lor (r \neq 0)$.

  By weak quasi-coherence, the canonical map
  % TODO: once this paper has its own definition of weak quasi-coherence, point this
  % reference at it (via \cref) instead of \cite{draft}.
  $(R/R_{D(r)})[1/r] \to (R/R_{D(r)})^{D(r)}$ is an equivalence \cite{draft}.
  We claim that $(R/R_{D(r)})^{D(r)} = 0$.  Indeed, if $r \neq 0$, then the
  predicate $(x = 0) \lor (r \neq 0)$ holds for every $x : R$, so $R_{D(r)} = R$ and
  hence $R/R_{D(r)} = 0$.  This gives a proof of $(r \neq 0) \to (R/R_{D(r)} = 0)$,
  and so every element of $(R/R_{D(r)})^{D(r)}$ is zero.

  It follows that $(R/R_{D(r)})[1/r] = 0$.
  In particular, the class of $1$ is annihilated by a power of
  $r$: there merely exists $k : \N$ with $r^k \in R_{D(r)}$, that is,
  $(r^k = 0) \lor (r \neq 0)$.
  This is equivalent to $(\exists k,\ r^k = 0) \lor (r \neq 0)$, and as a nilpotent
  element $r$ satisfies $\lnot\lnot(r = 0)$, we obtain
  $\lnot\lnot(r = 0) \lor \lnot(r = 0)$.
  As $r : R$ was arbitrary, we deduce that
  $\prod_{r : R} \big(\lnot\lnot(r = 0) \lor \lnot(r = 0)\big)$, a form of weak excluded
  middle.  The two disjuncts are mutually exclusive,
  so the truncation in $\lor$ can be dropped.  Recording which disjunct holds defines
  a function $\chi : R \to \Bool$, which takes different values at $r = 0$ and $r = 1$.
  Thus $\chi$ is not constant,
  which contradicts the connectedness of $R$ \cite[Proposition 1.2.2]{topology-draft}.
\end{proof}

% jdc
\begin{corollary}\label{cor:RDr-not-fin-adeq}
  It is impossible to prove that for every $r : R$ the module $R_{D(r)}$ is finitely
  adequate.
\end{corollary}

\begin{proof}
  This follows from \cref{prp:quot-RDr-not-wqc} and the fact that
  finitely adequate modules are closed under cokernels
  (\cref{prp:fin-adeq-cok-closure}).
\end{proof}

\begin{proposition}
  It is not the case that for all $r:R$ the modules $R^{D(r)}$ are finitely adequate.
\end{proposition}

\begin{proof}
  Suppose this is a family of finitely adequate modules.
  Then
  \[
    R[r^{-1}]^\ast = \{ a=(a_0,a_1,\dots) : R^{\mathbb N} \;|\; \forall k \geq 1.\; a_{k-1} = ra_k \}
  \]
  is finitely adequate again and thus also weakly quasi-coherent.
  We now have a commutative square
  \[
  \begin{tikzcd}
    (R[r^{-1}]^\ast)[r^{-1}] \ar[d, "\simeq"]\ar[r] & R[r^{-1}], \ar[d, "\simeq"] &[-25pt] \frac{a}{r^n} \mapsto \frac{a_0}{r^n} \\
    (R[r^{-1}]^\ast)^{D(r)} \ar[r, "\simeq"] & R^{D(r)}, & f \mapsto f_0
  \end{tikzcd}
  \]
  where the lower horizontal map is an equivalence with inverse
  \[
    b \mapsto (p \mapsto (b(p),r^{-1}b(p),\dots))\rlap{.}
  \]
  This is well-defined as $p$ witnesses the fact that $r$ is invertible.
  Accordingly, the upper horizontal map is an equivalence.
  The preimage of $\frac{1}{1}:R[r^{-1}]$ along this map is represented by an element $\frac{a}{r^n}$ such that $r^k(a_0-r^n)=r^k(r^{n+1}a_{n+1}-r^n)=r^{k+n}(ra_{n+1}-1)=0$ for some $k$.
  Since $R$ is local, we have $(ra_{n+1} \neq 0) \lor (ra_{n+1}-1 \neq 0)$, which readily implies that $(r \neq 0) \lor (r^{k+n} = 0)$.
  But then any element $r:R$ would either be invertible or nilpotent, which contradicts the fact that $R$ is connected.
\end{proof}

\rednote{I can also show $\prod_{r:R}R[r^{-1}]^\ast = 0$ and wonder if this is interesting/useful in any way?}

Next we prove that some of the modules defined above are tangential.
We'll make use of the following lemma.

\begin{lemma}\label{forall-distributes-over-lor}
Let $X$ be projective type such that every map to $\Bool$ is constant.
Let $P, Q : X \to \Prop$ be predicates.
Then $\forall x : X, P(x) \lor Q(x)$ is equivalent to $(\forall x, P(x)) \lor (\forall x, Q(x))$.
\end{lemma}

\begin{proof}
Since the two types are proposition, it suffices to give implications in both directions.
There is an obvious implication from right to left, so we are left to prove that
$\forall x : X, P(x) \lor Q(x)$ implies $(\forall x, P(x)) \lor (\forall x, Q(x))$.
So assume $\forall x : X, P(x) \lor Q(x)$.
Since $\lor$ is the propositional truncation of the coproduct, the fact that $X$ is projective
means that we merely have a map in $\prod_x P(x) + Q(x)$.
Since we are proving a proposition, we can drop the ``merely''.
The gives us a map $X \to \Bool$, which by assumption must be constant.
This implies that we have either $\prod_x P(x)$ or $\prod_x Q(x)$, as required.
\end{proof}

\begin{proposition}
For any type $U$, the modules $R_U$ and $R/R_U$ are tangential.
\end{proposition}

\begin{proof}
We first consider $R_U \defeq \sum_{x : R} (x = 0) \lor U$.
The type $\tangent{(R_U)}{0}$ is equivalent to
\[
  \sum_{f : \D(1) \rightarrow_\ast R} \forall \epsilon : \D(1), (f(\epsilon) = 0) \lor U .
\]
Since $\D(1)$ is projective (\cref{lem:disk-projective}) and all maps $\D(1) \to \Bool$
are constant (\rednote{Citation?}), we can apply \cref{forall-distributes-over-lor} to
get an equivalence to
\[
  \sum_{f : \D(1) \rightarrow_\ast R} (f = 0) \lor U ,
\]
where we have replaced $\forall \epsilon : \D(1), f(\epsilon) = 0$ with $f = 0$
and have used that $\D(1)$ is pointed to replace $\D(1) \to U$ with $U$.
Since $R$ is tangential, we can replace $\D(1) \rightarrow_\ast R$ with $R$,
giving
\[
  \sum_{x : R} (x = 0) \lor U ,
\]
which equals $R_U$.
It is not hard to check that the resulting equivalence is homotopic to the canonical map.

It follows from \cref{prp:lim-col-ext-tangential} that $R/R_U$ is tangential as well.
\end{proof}

Altogether there are approximately 15 modules above, five for each of
$V(r)$, $D(r)$ and $\lnot D(r)$.
(A couple turn out to be equal, and a couple were introduced that don't
come from the general construction.)
One can also take kernels or cokernels of the various vertical maps.

There are also some variations.  For example, we can consider $R_U'$, defined
using the predicate \mbox{$\lnot \lnot (x = 0) \lor U$} instead of $(x = 0) \lor U$.
When $U$ is false, this already produces a submodule that is not tangential
and is therefore not finitely adequate.
As $U$ varies, this gives more potential examples.
Similarly, we could define ${K^U}' := \sum_{x : R} (U \to \lnot \lnot (x = 0))$,
a slightly larger version of $K^U$.

We showed above that the families $R^{\lnot D(r)}$, $R/R_{D(r)}$, and $R_{D(r)}$ are not all
finitely adequate.
(It's also trivial that the family $R_{D(r)}'$ is not all finitely adequate, since
$R_{D(0)}'$ is not finitely adequate.)
\textbf{Can we show the same for the remaining families (such as $R/K^{D(r)}$, $R_{\lnot D(r)}$,
or $R_{V(r)}$), or that some of them have other bad properties?}
The technique in Theorem 3.2.1 of the topology draft might be helpful.
Note that the map $\varphi_r$ that appears above also appears there.

Methods for showing that an $R$-module $M$ is not finitely adequate:
\begin{itemize}
\item Show that the map $M \to M^{\ast\ast}$ is not an equivalence.
\item Show that $M$ is not wqc.
\item Show that $M$ is not tangential.
Unfortunately, for any $U$, the five modules associated to $U$
are all tangential, so this method won't work for them.
\item Show that $M$ is not infinitesimally linear.
\item Show that there exists an epi $e : C \to M$ and a map $f : A \to M$,
with $A$ and $C$ finitely co-presented, such that $f$ does not lift through $e$.
(See \Cref{maps-into-coherent-lift}.)
\item Show that there exists a mono $i : M \to C$ and a map $f : M \to A$,
with $A$ and $C$ finitely presented, such that $f$ does not extend over $i$.
(The dual of \Cref{maps-into-coherent-lift}.)
\item Finitely adequate implies not not finite-free \rednote{Citation?},
so it suffices to prove that $M$ is not finite free.
To show $\lnot (\text{for all $r : R$, $M_r$ is finitely adequate})$ for a family $M_r$,
I think you need to prove $\lnot (\text{for all $r : R$, not not $M_r$ is finite-free})$.
Unfortunately, when $U$ is a proposition, the five modules associated to $U$
are all not not finite free, so this method won't work for them.
\end{itemize}

\subsection{Questions (and some answers)}
\begin{enumerate}
\item Is dualization an anti-equivalence of finitely adequate modules?

      Yes.
\item Are finitely adequate modules closed under extension?

      If the quotient module is also finitely generated, then yes.
\item\label{ad-hom-closed} Are finitely adequate modules closed under $\Hom$?

      Yes, \cref{prp:fin-adeq-hom-closure}.
\item Are finitely adequate modules closed under $\_\otimes\_$?

      Yes, for finite free \(B\), by \cref{ad-hom-closed} and \(A\otimes B^\ast=\Hom(B,A)\).
\item Does exponentiating with closed propositions preserve finitely adequate?

      Yes, by partial answer to \cref{finite-exp-closed}.
\item\label{finite-exp-closed} Are projective/proper/finite-scheme products of finitely adequate modules finitely adequate?

      Partial answer:
      \begin{enumerate}[(i)]
      \item Let $X$ be a finite scheme, i.e. $X$ an affine scheme such that $R^X$ is a finitely presented $R$-module.
      For any finitely adequate-module $M:X\to\Mod{R}_{\mathrm{ad}}$ on $X$, $(x:X)\to M_x$ is finitely adequate: We can exponentiate the diagram witnessing that it is an finitely adequate-module and we can globalize the presentations of pointwise fp modules.
      Exponentiating is left exact and since $M$ is wqc and $X$ affine, it is also right exact.
      \end{enumerate}

\item Are the cohomology groups of finitely adequate module bundles on projective schemes finitely adequate?

      None so far. It seems a bit much to ask, but it would be really great for Serre-Duality, so it should be worth it to try to adapt e.g.\ \cite[19.1.3]{vakil}.

\item Is any finitely adequate-module quasi-coherent?

      No. The kernel $K$ of $2\cdot\_:R\to R$ can not be (strongly) quasi-coherent in general.
      So far there is only an external argument: \url{https://www.youtube.com/watch?v=mdjq91Gc6Lo} around 1:10:00 states that strongly quasi-coherent modules are invariant under pullback. But in general $K$ can change between trivial and non-trivial on different stages.
\item Does being finitely adequate depend only on the underlying type?  Maybe related to being an fppf sheaf?
\item What are examples of modules that are not finitely adequate?

      $R^\mathbb{N}$.  A direct sum of countable copies of $R$.  (Citations/proofs?)

      Are there some that are ``smaller'' in some sense?
      What about the ones mentioned in \cref{strange-modules}?

      \begin{lemma}
        \label{perfect-pairing-powerseries-polynomials}
        The pairing
        \[
          R^{\oplus\mathbb{N}} \times R^{\mathbb{N}} \to R, \;\;
          (a,b) \mapsto \langle a,b \rangle :\equiv \sum a_jb_j
        \]
        is perfect.
      \end{lemma}

      For a proof we give a constructivized and adapted version of the one given in \cite[Satz 1]{Specker1950}.
      This is a folklore theorem due to Ernst Specker and proof in loc.\ cit.\ (in particular) shows that $\mathbb{Z}^{\oplus\mathbb{N}}$ is isomorphic to $\Hom_{\mathbb{Z}}(\mathbb{Z}^{\mathbb{N}},\mathbb{Z})$.
      It uses the prime factorization in $\mathbb Z$, which we replace by a neat degree-counting argument using duality.

      \begin{proof}
      It is clear that $\vartheta':R^{\mathbb{N}} \to \Hom_R(R^{\oplus\mathbb{N}},R), b \mapsto (a \mapsto \langle a,b \rangle)$ is an equivalence and we only explain that the second induced map
        \[
          \vartheta:
          R^{\oplus\mathbb{N}} \to \Hom_R(R^{\mathbb{N}},R), \;\;
          a \mapsto \left(b \mapsto \langle a,b \rangle\right)
        \]
        is an equivalence.
        For it is clearly injective, we only verify surjectivity.
        Let $\lambda : R^{\mathbb{N}} \to R$ be an arbitrary $R$-linear map and define a sequence $a :\equiv (n \mapsto \lambda(e^n))$, where $e^n$ is the sequence given by $j \mapsto \delta_{nj}.$
        We will show that $a_n = 0$ for $n>>0$ and then finish the proof by verifying $\lambda = \langle a, - \rangle$.
        Define further a map
        \[
          f : R \to R, \;\;
          r \mapsto \lambda(1,r,r^2,r^3,\dots)\rlap{,}
        \]
        Duality tells us that $f$ is a polynomial.
        As we want to show a proposition, we may assume that $\deg f \leq d$ for some $d$.
        By linearity of $\lambda$ and for all $N:\mathbb{N}$, we have
        \[
          f(r) = a_0 + a_1r + a_2r^2 + \dots + a_{N-1}r^{N-1} + r^N\lambda(0,\dots,0,1,r,r^2,\dots)\rlap{,}
        \]
        where exactly the first $N$ entries in $\lambda(0,\dots,0,1,r,r^2,\dots)$ are zero.
        Comparing coefficients, we see that $a_N=0$ for $N \geq d+2$, hence $a$ is an element of $R^{\oplus\mathbb{N}}$.
        So it remains to check that $\varphi : \equiv \lambda - \langle a,- \rangle = 0$.
        For this let $b:R^{\mathbb{N}}$ be arbitrary and set
        \[
          g:R \to R, \;\;
          r \mapsto \varphi(b_0,b_1r,b_2r^2,\dots)\rlap{.}
        \]
        Since $\varphi(e^n)=0$, we can repeat the argument just applied to $f$ and see that all of the polynomials $x^n$ divide $g$.
        But then $g=0$ and in particular $0 = g(1) = \varphi(b) = \lambda(b) - \langle a,b \rangle$.
      \end{proof}
      \begin{corollary}
        The $R$-modules $R^{\mathbb{N}}$ and $R^{\oplus\mathbb{N}}$ are reflexive.
      \end{corollary}

        Since we know that $R^{\mathbb{N}}$ is not finitely adequate, we now know that the class of reflexive and finitely adequate $R$-modules are different.

      \begin{proof}
        We have a commutative diagram
        \[
        \begin{tikzcd}
          R^{\mathbb{N}} \arrow[r,"t"] \arrow[dr,"\vartheta'"'] & (R^{\mathbb{N}})^{\ast\ast} \arrow[d,"\vartheta^\ast"]
          \\
          & (R^{\oplus\mathbb{N}})^\ast
        \end{tikzcd}
        \]
        with $t$ the canonical double dual map and $\vartheta$, $\vartheta'$ as in the proof of \Cref{perfect-pairing-powerseries-polynomials}.
        As is shown there, these two maps are equivalences, implying that $t$ is as well.
        A similar argument works for $R^{\oplus\mathbb{N}}$.
      \end{proof}

\item What are examples of modules that are not infinitesimally linear/tangential?

      $\mathrm{Nil}(R)$ is infinitesimally linear but not tangential.

      Denote by $R[S]$ the free $R$-module generated by a set $S$.
      Let $M :\equiv R[\D(2)]/R[\D(1)\vee\D(1)]$ and say $\eta : \D(2) \to R[\D(2)]$ is the constructor map, which induces a pointed map $\tilde{\eta} : \D(2) \to M$.
      By construction we have $\tilde{\eta}|_{\{0\} \times \D(1)} = \tilde{\eta}|_{\D(1) \times \{0\}} = 0$ but since $\D(1)\vee\D(1) \lhook\joinrel\to \D(2)$ is provably not surjective, we have $\tilde{\eta} \neq 0$.
      Hence $M$ is not infinitesimally linear (and in particular not finitely adequate).

      If $R$ has characteristic $p$, then $\hood{R,0}{p-1}$ is not tangential. Its tangent space is $R$ by the same above reasoning.
\end{enumerate}
