
\begin{definition}
Let $M$ be the commutative $1$-monoid of finite dimensional vector spaces, that is:
\[M = \Sigma_{k:\N} BU_k\]
with $\oplus$ as addition.
\end{definition}

We will define three simplicial types. 

\begin{remark}
Given a simplicial type $X$ we define its geometric realisation $|X|$ by:
\[|X| = \mathrm{coend}_k X_k\times\Delta^k\]
We cannot prove $|X|$ exists for arbitrary simplicial types, but it does exist for simplicial sets.

At least in favorable cases, we expect $\shape |X| = \mathrm{colim}_k \shape X_k$, since inclusions $\Delta^k \subset \Delta^{k+1}$ are all $\shape$-equivalence.
\end{remark}

\begin{definition}
We define a simplicial groupoid $H$ by $H_k = M^k$, with inner face maps sending $(m_1,\cdots,m_k)$ to $(m_1,\cdots,m_i+m_{i+1},\cdots,m_k)$ and the outer face maps forgetting extremal elements.
\end{definition}

The simplicial groupoid $H$ is intuitively a delooping of $M$. This means we expect $\shape |H|$ to be pointed connected, and $\Omega(\shape |H|)$ to be the group completion of $M$, which we expect to be $\Z\times B\shape U$. 

\begin{definition}
We define the simplicial set $F_n$ by as the set $n$ tuples of pairwise orthogonal finite support projection on $\C^\infty$. The face maps defined as for $H$.
\end{definition}

\begin{proposition}
We have that $|F| = U$.
\end{proposition}

\begin{proof}
We have that $\Delta_n = \{t_1,\cdots,t_n:\I\ |\ t_1\leq \cdots\leq t_n\}$.

Consider the map:
\[F_n\to U\] 
\[((E_1,\cdots,E_n),(t_1,\cdots,t_n)) \mapsto \mathrm{exp}(2i\pi(t_1E_1+\cdots+t_nE_n))\]
It easy to check it is define a map $|F|\to U$, that it is an equivalence is the spectral theorem.
\end{proof}

\begin{definition}
We define the simplicial sets $G$ by $G_n = (\Sigma_{k:\N}\Sigma_{V:BU_k}V\subset \C^\infty)^n_{orth}$ where the $orth$ means that the images in $\C^\infty$ are pairwise orthognal. The face maps defined as for $H$.
\end{definition}

\begin{lemma}
We have $F=G$.
\end{lemma}

\begin{proof}
Finite support projection on $\C^\infty$ correspond to finite dimensional subspace of $\C^\infty$.
\end{proof}

\begin{lemma}
The obvious forgetful map $G\to H$ is levelwise $\shape$-contractible.
\end{lemma}

\begin{proof}
The key point is that given $V\subset \C^\infty$ and $W$ a finite dimensional vector space, the type:
\[W\subset V^\perp\]
is $\shape$-contractible. Fibers of maps $G_n\to H_n$ are $\Sigma$-types of types of this form so we conclude.
\end{proof}

Therefore we expect the map $|F| \to |H|$ to be a $\shape$-equivalence. We have $|F| = U$, so we would essentially need something like $\shape |H| = B(\Z\times B\shape U)$ to conclude. Another problem is of course that simplicial colimits do not exists.

