%
%\begin{lemma}
%Let $S$ be Stone and $C\subseteq S$. TFAE: 
%\begin{itemize}
%  \item $C$ is the complement of a closed subset. 
%  \item $C$ is the countable union of decidable subsets. 
%\end{itemize}
%\end{lemma}
%\begin{proof}
%  We claim that for $(A_n)_{n:\mathbb N}$ a family of decidable subsets, 
%  we have 
%  $(\bigcap A_n)^C = \bigcup (A_n^C)$. 
%  The claim then follows from the fact that a complement of a decidable subset is decidable, 
%  together with \Cref{propClosedAlternativeDefinitions}.
%  
%  Clearly if $x \in \bigcup(A_n^C)$, then 
%  there is an $n$ such that $x\in A_n^C$, 
%  thus it is not the case that $x\in A_n$ for all $n:\mathbb N$. 
%  Thus $x\in (\bigcap A_n)^C$. 
%  Thus $\bigcup (A_n^C) \subseteq (\bigcap A_n)^C$. 
%
%  For the converse direction, we'll use Markov's principle. 
%  Suppose that 
%  $x\in (\bigcap A_n)^C$. 
%  Consider the sequence $\alpha$ such that 
%  $\alpha(i) = 1$ iff $i$ is the first index such that $x\notin A_i$. 
%  As $A_n$ is decidable, this sequence is well-defined. 
%  If $\alpha(i) = 0$ for all $i:\mathbb N$, then 
%  $x\notin A_i$ for all $i:\mathbb N$, 
%  hence $x\in (\bigcap A_n)$
%
%  As $x\in (\bigcap A_n)^C$, it is not the case that 
%  $\alpha(i) = 0$ for all $i:\mathbb N$. 
%
%
%  Then there exists an $n$ such that $x\notin A_n$, so $x\notin (\bigcap A_n)$. 
%\end{proof}
%
%\begin{lemma}
%  For $S$ stone and $C\subseteq S$, TFAE:
%  \begin{itemize}
%    \item $C^C$ is open. 
%    \item $C$ is closed. 
%  \end{itemize}
%\end{lemma}
%\begin{proof}
%  Assume $x\in C$ for $C$ the complement of a countable union of decidable subsets. 
%  so $x\in (\bigcup A_n)^C$. 
%  Then for every $n:\mathbb N$, we have 
%  $x\notin A_n$, thus $x\in A_n^C$. 
%  Therefore $x \in \bigcap(A_n^C)$. 
%
%  Conversely, let $x\in \bigcap (A_n^C)$. 
%  So for 
%  By Markov's principle, there exists an $n$ with 
%  $x\notin A_n^C$, so $x\in A_n$ for 
%\end{proof}
%  
\begin{definition}
  Let $S$ be Stone, $C\subseteq S$. 
  Then $C$ is open if it is the countable union of decidable subsets. 
\end{definition}
\begin{lemma}
  For $S$ Stone and $C\subseteq S$, 
  $C$ is closed iff it's complement is open 
  and $C$ is open iff it's complement is closed. 
\end{lemma}
\begin{proof}
  This follows from the fact that the complement of a decidable subset is decidable and 
  \Cref{LemDecidableSubsetsDeMorgan}.
\end{proof}
\begin{lemma}
  For $S$ Stone, any cover by opens merely has a finite subcover.
\end{lemma}
\begin{proof}
  Let $S= \bigcup_{i:I} A_i$ be a cover of $S$ by open sets. 
  Assume furthermore $S= Sp(B)$. 
  As every open is the union of decidable subsets, we may assume $A_i$ decidable, 
  and thus corresponding to points $a_i \in B$. 
  These points are such that $1 = \bigvee_{i:I} a_i$. 
  As $B$ is countably presented, it is countable. 
  Thus $(a_i)_{i:I}$ is a countable set. 
  The morphism $I\to B$ is surjective, and as we're proving a proposition,
  we may use type-theoretic AC to give 
  a countable subset $I_0 \subseteq I$ such that $\bigvee_{i:I_0} a_i = 1$ as well. 
  So $S = \bigcup_{i:I_0} A_i$ for $I_0$ countable. 
\end{proof}

\begin{lemma}
  For $S$ Stone, any collections of closed sets satisfying the finite intersection property 
  has a merely inhabited intersection. 
\end{lemma}
\begin{proof}
  Suppose that $a_i$ is a collection of points such that $a_i \wedge a_j \neq 0$ whenever $i\neq j$. 
  We claim that $\bigwedge a_i \neq 0$. 
  Suppose $\bigwedge a_i = 0$. 
\end{proof}


\begin{definition}
We define a type $X$ to be compact Hausdorff iff 
there is a surjection $e:S\to X$ for $S$ Stone. 
%
A subtype $C\subseteq X$ is closed respectively open iff it's pre-image under $e$ is. 
\end{definition}

\begin{lemma}
  Let $X$ be a Compact Hausdorff type, 
  and suppose that $(A_i)_{i:I}$ is a collection of opens in $X$ such that 
  $X = \bigcup_{i:I} A_i$. 
  There then exists a finite subset $I_0\subseteq I$ with 
  $X = \bigcup_{i:I_0} A_i$. 
\end{lemma} 
\begin{proof}

\end{proof}

\begin{lemma}
  In a Compact Hausdorff space, the complement of an open is closed, and the complement of a closed is open. 
\end{lemma}
\begin{proof}
  Let $e : S \to X$ be a surjection from a Stone space, 
  and let $(A_n)_{n:\mathbb N}$ be a countable family of decidable subsets in $S$. 

  First, we claim that 
  $X - \bigcup_{n:\mathbb N} e(A_n)$
  is closed in $X$. 

  Note that 
  $
  X - \bigcup_{n:\mathbb N} e(A_n) 
  = 
  e(S) - e(\bigcup_{n:\mathbb N} A_n)
  $

\end{proof}

\begin{lemma}
  Whenever $X$ is compact Hausdorff, $F_0, F_1$ are closed and disjoint, 
  there exist $G_0, G_1$ disjoint clopen such that 
  $F_i \subseteq X - G_{1-i}$ and $G_0 \cup G_1 = X$. 
  
\end{lemma}
