In this section we use $\widetilde{X}$ to denote the formally étale replacement of $X$. We assume $B\widetilde\A^\times$ is $\A^1$-local. We don't know if this holds over any base in the model, but we think this holds over a base field. 

\begin{remark}
It is enough to assume $H^1(\A^1,\widetilde\A^\times) = 0$ or equivalently $H^1(\widetilde\A^1,\widetilde\A^\times)=0$. Indeed we $\widetilde\A^\times$ is $\A^1$-local so $B\widetilde\A^\times$ is $\A^1$-separated, and the cohomology condition means it is $\A^1$-smooth.
\end{remark}

Moreover we use the so-called refined definition of motivic homotopy groups, meaning:
\[\pi_n^{\A^1}(X) = \Omega^n(\shape_nX)\]

\begin{lemma}\label{smooth-A1-equivalent-etale-replacement}
If $X$ is a smooth scheme then the map:
\[X\to \widetilde X\]
is $\A^1$-connected.
\end{lemma}

\begin{proof}
Since $X$ is smooth the map:
\[X\to \widetilde X\]
is surjective by \cref{unramifiedReplacementEtaleForSmooth}. So any of its fiber is merely equivalent to $N_\infty(x)$ for some $x:X$. By \cref{smooth-scheme-manifold} any such $N_\infty(x)$ is merely equivalent to $N_\infty(0)$ in some $\A^n$, but these are $\A^1$-connected by \cref{basic-A1-connected-types}.
\end{proof}

\begin{lemma}\label{A1-cover-projective}
Assuming that $B\widetilde\A^\times$ is $\A^1$-local, we have that for all $n$ the map:
\[\widetilde \A^{n+1}/\{0\} \to \widetilde\bP^n\]
is an $\A^1$-cover with fiber $\widetilde\A^\times$.
\end{lemma}

\begin{proof}
The considered map is an $\widetilde\A^\times$-torsor so we can conclude using \cref{torsor-and-modalities}.
\end{proof}

\begin{lemma}\label{punctured-space-connected}
Assume $n\geq 2$, then we have that $\widetilde \A^{n+1}/\{0\}$ is $\A^1$-(n-1)-connected, meaning that:
\[\shape_{n-1}(\widetilde \A^{n+1}/\{0\}) = 1\]
\end{lemma}

\begin{proof}
By \cref{smooth-A1-equivalent-etale-replacement} we have that $\widetilde \A^{n+1}/\{0\}$ is $\A^1$-equivalent to $\A^{n+1}/\{0\}$, but by \cref{free-module-minus-point-shape} this is $\A^1$-equivalent to $(\A^\times)^{*(n+1)}$. But this type is $(n-1)$-connected as for any pointed type $X$ the join $X^{*n}$ is $n-2$-connected. Therefore it is $\A^1$-$(n-1)$-connected.
\end{proof}

\begin{proposition}\label{pi1-projective-2+}
Assuming that $B\widetilde\A^\times$ is $\A^1$-local, we have that:
\[\pi^{\A^1}_1(\bP^n) = \widetilde\A^\times\]
for all $n\geq 2$ and that:
\[\pi^{\A^1}_1(\bP^\infty) = \widetilde\A^\times\]
\end{proposition}

\begin{proof}
First we treat the case of $\bP^\infty$. By \cref{shape-projective-infinity} we have that $\bP^\infty$ is $\A^1$-equivalent to $B\A^\times$, which is itself $\A^1$-equivalent to $B\widetilde\A^\times$. So we have that:
\[\pi_1^{\A^1}(\bP^\infty) = \pi_1^{\A^1}(B\widetilde\A^\times)\]
but since $B\widetilde\A^\times$ is simply connected and assumed $\A^1$-local, we have that:
\[\pi_1^{\A^1}(B\widetilde\A^\times) = \Omega B\widetilde\A^\times = \widetilde\A^\times\]

Now assume $n\geq 2$. By \cref{smooth-A1-equivalent-etale-replacement} we know that:
\[\pi_1^{\A^1}(\bP^n) = \pi_1^{\A^1}(\widetilde\bP^n)\]
Then by \cref{A1-cover-projective} we have an $\A^1$-covering: 
\[\widetilde\A^\times \to \widetilde \A^{n+1}/\{0\} \to \widetilde\bP^n\]
But by \cref{punctured-space-connected} we have that $\widetilde \A^{n+1}/\{0\}$ is $\A^1$-1-connected, so by \cref{universal-cover-contractible} the cover is universal and by \cref{universal-cover-pi1} we can conclude that:
\[\pi_1^{\A^1}(\widetilde\bP^n) = \widetilde\A^\times\]
\end{proof}

What about $\bP^1$?

\begin{proposition}
Assuming that $B\widetilde\A^\times$ is $\A^1$-local, we have an exact sequence:
\[0\to \pi_1^{\A^1}(\A^2/\{0\}) \to \pi_1^{\A^1}(\bP^1) \to \widetilde\A^\times\to 0\]
\end{proposition}

\begin{proof}
Very similar to \cref{pi1-projective-2+} except we use \cref{connected-cover-pi1} instead of \cref{universal-cover-pi1}, and we need to prove that $\shape_1\A^2/\{0\}$ is $0$-connected. But it is $\A^1$-equivalent to $\A^\times * \A^\times$ which is $0$-connected, and we know that the map $X\to \shape_1X$ is surjective so $\shape_1\A^2/\{0\}$ is $0$-connected as well.
\end{proof}

 