
\rednote{META: This section is still very incomplete, but expected to work out with high level of confidence
(at least in the case of the second author).}

\subsection{General local resolutions}

\rednote{TODO: For the vanishing result and join-based chech cohomology, we also use what is explained below.
That should somehow be consolidated/brought into the right order.}

Among 1-truncated $\partial$-functors, $H^0, H^1$, i.e. the zeroth and first cohomology groups defined in terms of Eilenberg-MacLane spaces, will always be universal.
We will show this, by constructing local resolutions for $(H^0,H^1)$ in the sense of \cref{local-resolution}.
The construction will follow a general pattern,
which we will also use in the following sections for all other resolutions.
What follows, is an explanation in more classical terms -- a reader not familiar with those,
can safely skip that explanation, since the construction we use, will be quite simple
and can be understood without the classical notions of torsors or fibre bundles.

Let $X$ be a type and $A:X\to \AbGroup$.
An element $\chi:H^1(X,A)$ can be merely represented by a map $T:(x:X)\to K(A_x,1)$.
If we use the particular implementation of the deloopings $K(A_x,1)$ as
$A_x$-torsors, $T_x$ will be a set with an action and it is natural to view $T$ as a bundle over $X$.
Let us relax the usual notion of fibre bundle a bit, to also admit the case of our $A$-torsors,
i.e. let the following be the type of $A$-fibre bundles over $X$:
\[ \sum_{T:X\to\mathcal U}\|T_x=A_x\|\]
Then, $A$-torsors will in particular also be $A$-fibre bundles.

A canonical trivialization for fibre bundles with constant prescribed fiber
is given in (\cite{cherubini-cartan})[Definition 4.9, Definition 4.11] -- but this works for the more general notion as well.
The canonical trivialization is given by
\[ V_T:\equiv \sum_{x:X}T_x=A_x \]
Then, from the definition above, we get that $\pi_1:V_T\to X$ is surjective
and the second projection will give a trivialization witness for the pullback of $T$ along $\pi_1$.

Now, since the local resolution has to be something over $X$, we have to push-forward the construction above.
But that really just means we have to take a dependent product instead of a sum.
So the resulting dependent group is just:
\[ x\mapsto A_x^{(T_x=\ast)} : X\to\AbGroup\]
The canonical map $A_x\to A_x^{(T_x=\ast)}$ maps an element $a_x:A_x$ to the function $p\mapsto a_x$.
Since $T_x=\ast$, this map will be an embedding.

For a more general $T:(x:X)\to K(A_x,l)$,
the type $\|T_x=\ast\|_0$ will be trivial if $l>1$ and therefore $A_x\to A_x^{(T_x=\ast)}$ will be an equivalence,
since $A_x$ is 0-truncated.
This means the same construction will \emph{not} work for cohomology groups above degree 1,
with coefficients in Eilenberg-MacLane spaces.
Another way to phrase the problem is,
that the spectrum $K(A_x,\_)^{(T_x=\ast)}$ fails to be an Eilenberg-MacLane spectrum.
This happens, if and only if, ${T_x=\ast}$ has non-trivial cohomology.
So one thing we can use to resolve higher cohomology classes, are covers of $X$ with cohomologically trivial fibers,
which we will do in the next section.
Now we will show, how we can use the general construction for degree 1 to get all requirements of \cref{local-resolution}:

\begin{lemma}
  \label{general-1-resolution-exists}
  Let $A:X\to\AbGroup$ and $\chi:H^1(X,A)$.
  Then there merely is a short exact sequence $\mathcal{S}_\chi$:
  \begin{center}
    \begin{tikzcd}
      0\ar[r] & A\ar[r,"m_\chi"] & M_\chi\ar[r] & C_\chi\ar[r] & 0
    \end{tikzcd}
  \end{center}
  such that for any other short exact sequence $\mathcal{S}=A\to R\to S$
  such that $\chi$ is mapped to zero in $H¹(X,R)$ and any morphism $f:A\to B$ we have
  a zig-zag:
  \begin{center}
    \begin{tikzcd}
      A\ar[r]\ar[d,"f"] & R\ar[r]\ar[d] & S\ar[d] \\
      B\ar[r] & M_{f,\mathcal{S}}\ar[r] & C_{f,\mathcal{S}} \\
      B\ar[r,"m_{f(\chi)}"]\ar[u,equal] & M_{f(\chi)}\ar[r]\ar[u] & C_{f(\chi)}\ar[u]
    \end{tikzcd}
  \end{center}
\end{lemma}

\begin{proof}
  As explained above, we merely have $T:(x:X)\to K(A_x,1)$ with $|T|_0=\chi$ and the definition
  $M_\chi\colonequiv ((x:X)\mapsto A_x^{(T_x=\ast)}$ together with the diagonal map $(a\mapsto (x, p\mapsto a_x)):A\to M_\chi$,
  gives a monomorphism $A\to M_\chi$.
  So we can take the cokernel, to a short exact sequence as required.
  $m_\chi^\ast(\chi)$ is zero by $x\mapsto \id_{(T_x=\ast)}:(x:X)\to T_x=\ast$.
  Note that this construction is well-defined in the sense that
  for another $T'$ with $|T'|=\chi$, we merely have $\|T=T'\|$ and therefire an isomorphism between the resulting sequences.

  Now, let $\mathcal{S}=A\to R\to S$ be a short exact sequence
  such that $\chi$ is mapped to zero in $H¹(X,R)$ and $\varphi:A\to B$ any morphism.
  For $T:(x:X)\to K(A_x,1)$ with $|T|=\chi$ and $T'\colonequiv (x\mapsto K(\varphi_x,1)(T_x))$ 
  a zig-zag can be constructed,
  whose maps we will describe below the diagram: 
  \begin{center}
    \begin{tikzcd}
      A\ar[r]\ar[d,equal] & R\ar[r]\ar[d,"\Delta"] & S\ar[d,dashed] \\
      A\ar[r,"\varphi\Delta"]\ar[d,equal] & (x\mapsto R_x^{T_x=\ast})\ar[r] & \coker(\varphi\Delta) \\
      A\ar[r,"\Delta"]\ar[d,"\varphi"] & (x\mapsto A_x^{T_x=\ast})\ar[r]\ar[d]\ar[u] & \coker(\Delta)\ar[d, dashed]\ar[u,dashed] \\
      B\ar[r,"\Delta'"] & (x\mapsto B_x^{T_x=\ast})\ar[r] & \coker(\Delta') \\
      B\ar[r,"\Delta''"]\ar[u,equal] & (x\mapsto B_x^{T'_x=\ast})\ar[r]\ar[u] & \coker(\Delta'')\ar[u,dashed]
    \end{tikzcd}
  \end{center}
  The maps in the middle column are all given by postcomposition with given maps,
  except for the last map, which is given by precomposition with a map
  $T_x=\ast\to T'_x=\ast$ given by using the pointed map $K(\varphi_x,1)$.
  All maps in the right column, are then induced by the universal property of cokernels.
  As noted above, the last row is isomorphic to any $\mathcal{S}_\chi$,
  so the zig-zag does indeed satisfy the specification from \cref{local-resolution}.
\end{proof}

\begin{theorem}
  $H^{\leq 1}$ is a 1-truncated, universal $\partial$-functor.
\end{theorem}

\begin{proof}
  By \cref{general-1-resolution-exists} we have local resolutions for $H^{\leq 1}$,
  we can apply \cref{thm:universal}.
\end{proof}

\subsection{Local resolutions for schemes}

\begin{definition}
  Let $X,Y$ be schemes and.
  \begin{enumerate}[(a)]
  \item For $M:Y\to\Mod{R}$ and $f:X\to Y$ let $f^*M:\equiv (x:X)\mapsto M_{f(x)}$.
  \item For $M:X\to\Mod{R}$ and $f:X\to Y$ let $f_*M:\equiv (y:Y)\mapsto \prod_{x:\fib_f(y)}M_{\pi_1(x)}$.
  \end{enumerate}
\end{definition}

Both operations preserve weakly quasi coherent modules by \cite{draft}[Theorem 9.1.11].
At the heart of the construction of local resolutions below,
is what is called \notion{Zariski-local choice} in \cite{draft} and justified as an axiom there.
A special case is local-triviality of cohomology classes:

\begin{axiom}
  Let $X=\Spec A$ be an affine scheme and $M:X\to\Mod{R}$.
  For $n>0$ and each $\chi:\prod_{x:X}K(M_x,n)$ there merely is a Zariski cover,
  i.e. coprime
  $f_1,\dots,f_n:A$ such that on each subtype $D(f_i):\equiv (x:X)\mapsto D(f_i(x))$,
  $\chi$ is trivial.
\end{axiom}

With that, there merely are finite covers of schemes trivializing any $M$-cohomology class $\chi$.
Let us denote the coproduct of such a cover with $U_\chi$,
so we have a surjection $u_\chi:U_\chi\to X$ such that $\prod_{x:U_\chi}\chi_x=M_x$.
If we started with a weakly quasi coherent $M$,
we get an injective map of weakly quasi coherent modules:
\[
  M_x \to M_x^{\fib_{u_\chi}(x)}
\]
where the domain is weakly quasi coherent, since it is $({u_\chi}_*u_\chi^*M)_x$.

To get a resolution from that, we need to see that cokernels of monomorphisms
of weakly quasi coherent modules are weakly quasi coherent.
In symbols, for $N\subseteq M$ one of those morphisms, we need:
\[
  (M/N)_f=(M/N)^{D(f)}.
\]
by algebra $(M/N)_f=M_f/N_f$.
This means we are done, if $(M/N)^{D(f)}=M^{D(f)}/{N^{D(f)}}$.
To see this holds, let us consider $0\to N\to M\to M/N\to 0$ as a short exact sequence of dependent modules,
over the subtype of the point $D(f)\subseteq 1=\Spec R$.
Then, taking global sections, we have an exact sequence
\[
 0\to N^{D(f)}\to M^{D(f)}\to (M/N)^{D(f)}\to H^1(D(f),M)
\]
-- but $D(f)=\Spec R_f$ is affine,
so the last term is 0 and $(M/N)^{D(f)}$ is the cokernel $M^{D(f)}/N^{D(f)}$.
So we know that dependent wqc modules over a scheme,
always merely have local resolutions consisting of dependent wqc modules.

By \cref{vanishing-conjecture},
the types $K(M_x,n)^{U_\chi}$, where $M_x$ is wqc and $n>0$ are $0$-connected
-- note that $M_x$ is weakly quasi coherent on $U_\chi$, since it is the push-forwad
of $M_x$ along the map $U_\chi\to 1$.

This means that $\left(K(M_x,n)^{U_\chi}\right)_{n:\N}$ is an Eilenberg-MacLane spectrum.
So we have found resolving sequences for all gerbes on a scheme with coefficients in weakly quasic coherent modules.


\subsection{Local resolutions for \v{C}ech-Cohomology}

Let $X$ be a fixed set and $\{U\}=(U_0,\dots,U_n)$ a fixed cover of $X$.
If $\{U\}$ is acyclic, then the \v{C}ech Cohomology of weakly quasi coherent modules on $X$
will be a universal $\partial$-functor.

The local resolutions can be constructed using the \notion{\v{C}ech-sheaf construction}.