% latexmk -pdf -pvc main.tex
% latexmk -pdf -pvc -interaction=nonstopmode main.tex
\documentclass{../util/zariski}

\title{Differential Geometry of Synthetic Schemes}
\author{Felix Cherubini$^1$, Matthias Ritter$^1$, Hugo Moeneclaey$^1$ and David Wärn$^1$}
\date{$^1$ University of Gothenburg and Chalmers University of Technology }

\begin{document}

\maketitle

\begin{abstract}
  Synthetic algebraic geometry is a new approach to algebraic geometry. It consists in using homotopy type theory extended with three axioms, together with the interpretation of these in a higher version of the Zariski topos, in order to do algebraic geometry internally to this topos. In this article we make no essential use of the higher structure of types, so that we could alternatively use the traditional Zariski 1-topos.
  
  We give new synthetic definitions of étale, smooth and unramified maps between schemes.
  We prove the usual characterizations of these classes of maps in terms of injectivity, surjectivity and bijectivity of differentials. We also show that the tangent spaces of smooth schemes are finite free modules.
  Finally, we show that unramified, étale and smooth schemes can be understood very concretely, indeed they admit the expected local algebraic description.
\end{abstract}

\tableofcontents

\section*{Introduction}
\input{../overview/history-and-introduction.tex}
\paragraph{Contribution and organization of the article. }
\input{contribution-and-organization.tex}
\paragraph{Acknowledgements.}
\input{acknowledgements.tex}

\section{Formally étale, unramified and smooth types}
\input{etale-unramified-smooth-type.tex}

\section{Linear algebra and tangent spaces}
\input{linear-algebra.tex}

\section{Unramified schemes}
\input{unramified-scheme.tex}

\section{Smooth and étale schemes}
\input{etale-smooth-scheme.tex}

\pagebreak
\appendix
\section{Appendix}
\input{appendix.tex}

\printindex

\printbibliography

\end{document}
