% latexmk -pdfxe -pvc -interaction=nonstopmode main.tex
\documentclass{../util/zariski}

\title{\v{C}ech Cohomology in Homotopy Type Theory}

\author{Ingo Blechschmidt, Felix Cherubini and David Wärn}

\begin{document}

\maketitle

\begin{center}
  \large{Press CRTL+F5 from time to time, to clear cached versions}
  \large{(if you are viewing these notes online)}
\end{center}

\tableofcontents

\section*{Introduction}
This is an incomplete draft on work in progress by Ingo Blechschmidt, Felix Cherubini and David Wärn.

In pure mathematics,
it is a common practice to simplify questions about complicated objects
by assigning them more simply objects in a systematic way that faithfully represents some features of interest.
One particular, but still surprisingly broad applicable instantiation of this appraoch,
is the assignment of a sequence of abelian groups, the cohomology groups, to spaces, sheaves and other things.
Over the last century, cohomology was first discovered in concrete examples, then generalized and streamlined,
a process that culminated in the presentation of cohomology groups as mapping spaces in higher toposes.

This is a representation, we can easily and elementary use through the interpretation of homotopy type theory in higher toposes.
In \cite{evan} results about cohomology theories like the Mayer-Vietoris-Sequence were proven and computations were carried out,
in \cite{floris}, the Serre-Spectral-Sequence was constructed and used.
The latter also introduced cohomology with non-constant coefficients,
which are the right level of generality for the applications we have in mind.
We are particularly interested in computing cohomology groups of sheaves in algebraic geometry,
which can be done synthetically using the foundation laid out by \cite{foundations-draft}
building on work and ideas of \cite{ingo}, \cite{kock}, \cite{david-myers}.

In this setup, the basic spaces in algebraic geometry, schemes, are just sets with a particular property \cite{foundations-draft}[def of scheme],
and instead of sheaves on a type $X$, we consider, more generally maps $A:X\to\AbGroup$ to the type of abelian groups.
The cohomology groups are then defined as dependent function types with values in Eilenberg-MacLane-Spaces
\[ H^n(X,A)\colonequiv \|(x:X)\to K(A(x),n)\|_0\]
-- a definition first suggested by \cite{mikes-blogpost}.
Due to its simplicity, this is very convenient to work with.
But - which is also a problem of the elegant formulation in higher toposes -
it is unclear how to make computations.
The problem, at least for a large class of calculations, can roughly be split into two parts:
First, one has to show that some large class of cohomology groups on simple spaces is trivial,
second, show that on spaces which are build from theses simple spaces,
cohomology can be computed by \v{C}ech cohomology.

\ignore{
  PROPOSED CONTENT:

  hott preliminaries
  the mayer vietoris sequence
  basic chech cohomological results
  * def of chech cohomology
  * vanishing of H^{n+1} for a space with acyclic cover with n pieces?
  example: synthetic algebraic geometry
  * repetition of basic facts on wqc modules
  * triviality of H^n
  direct chech cohomology
  * proof so far
  derived functors
  * universality of H^n on some schemes
  * universality of chech-H^n
  universality of H^n and chech-H^n/construction of local resolutions
  * for chech cohomology on a space with acyclic cover
  * for a scheme with cover with cohomologically trivial fibers and EM-Cohomology with values in wqc modules
  examples?
  * line bundles on P^n?
}


\section{The Mayer-Vietoris-Sequence}
\input{mayer-vietoris.tex}

\section{\v{C}ech cohomology}
\input{chech.tex}

\section{Cohomology of affine schemes}
\input{affine-vanishing.tex}

\section{\v{C}ech cohomology of a join}
\input{cech-join.tex}

\section{$\partial$-Funtors}
\input{delta-fun.tex}

\section{Construction of local resolutions}
\input{resolutions.tex}

\printindex

\printbibliography

\end{document}
