Usually, in some of the definitions below,
there is the additional condition that types are sheaves for the fppf topology.
We will just ignore this condition for now.

\begin{definition}
  A set $X$ is an \notion{algebraic space},
  if $x=_Xy$ is a scheme for all $x,y:X$ and
  there merely is a scheme $U$ with a formally étale surjection onto $X$.
\end{definition}

So any scheme is an algebraic space.

\begin{lemma}
  Let $X,Y$ be algebraic spaces and $f:X\to Y$ a map.
  Then there merely are schemes $U,V$ together with formally étale surjections
  $u:U\to X$, $v:V\to Y$ and $\widetilde{f}:U\to V$ such that
  \begin{center}
    \begin{tikzcd}
      U\ar[r,"\widetilde{f}"]\ar[d,"u"] & V\ar[d,"v"] \\
      X\ar[r,"f"] & Y
    \end{tikzcd}
  \end{center}
\end{lemma}

\begin{proof}
  We merely have a formally étale surjections $v:V\to Y$ and $u:U\to X$ by assumption.
  Let $P'$ be the iterated pullback:
  \begin{center}
    \begin{tikzcd}
      P'\ar[r]\ar[d,"p'"] & P\ar[r]\ar[d,"p"] & V\ar[d,"v"] \\
      U\ar[r,"u"] & X\ar[r,"f"] & Y
    \end{tikzcd}
  \end{center}
  Then $P=(x:X)\times W_x$, with $W_x\colonequiv (z:V)\times f(x)=v(z)$.
  As a dependent sum of schemes, $W_x$ is a scheme.
  For the same reason, $P'=(x:U)\times W_{u(x)}$ is a scheme.
  As itereted pullback of a formally étale surjection,
  $p'$ is a formally étale surjection and
  therefore also the composition with $u$.
\end{proof}

\begin{definition}
  A 1-type $X$ is a \notion{algebraic stack},
  if $x=_Xy$ is an algebraic space for all $x,y:X$ and
  and there merely is a scheme $U$ with a formally smooth surjection $u$ onto $X$.
  If, in addition, there is a
  formally étale surjection $u:U\to X$,
  $X$ is called a \notion{Deligne-Mumford stack}.
\end{definition}

\begin{proposition}
  Let $G$ be an étale group scheme acting on a scheme $X$,
  then the homotopy quotient $X//G$ is a Deligne-Mumford stack.
\end{proposition}

\begin{proof}
  The fibers of $X\to X//G$ are merely equivalent to $G$
  and therefore étale.
  This means the map $X\to X//G$ is formally étale.
  Let the action of $G$ be given by a dependent type
  $\rho:BG\to \Sch$.
  The identity types in $X//G$ are of the form:
  \begin{align*}
    &(x,p)=(x',p') \\
    \simeq& \sum_{g:x=_{BG}x'}\mathrm{transport}_{\rho}(g)(p)=_Xp'
  \end{align*}
  So as a dependent sum of schemes over a scheme,
  the identity types are always scheme. 
\end{proof}