Here we examine the links between the \'etale and fppf topology. 

\begin{definition}
The fppf topology consists of the set of $\Spec(A)$ for $A$ a faithfully flat algebra, i.e.\ such that tensoring with $A$ preserve and reflect exactness.
\end{definition}

Before a full fledged development of the fppf topology, it would be nice to have the following:

\begin{conjecture}
A type is an fppf sheaf if and only if it is $\propTrunc{\Spec(R[X]/P)}$-local for all $P:R[X]$ monic non-constant.
\end{conjecture}


\subsection{Flatness and faithful flatness}

\begin{lemma}
Let $M$ be a module, TFAE:
\begin{enumerate}[(i)]
\item $M$ is flat.
\item For all $I$ fg ideal in $R$, we have that $I\otimes M\to M$ is an injection.
\end{enumerate}
\end{lemma}

\begin{proof}
This is Lombardi Quitt\'e Theorem VIII.1.11.
\end{proof}

\begin{lemma}
Let $A$ be a flat algebra, TFAE:
\begin{enumerate}[(i)]
\item $A$ is faithfully flat.
\item For all $R$-module $M$ if $A\otimes M=0$ then $M=0$.
\item For all finitely generated ideal $I\subset R$, if $A\otimes R/I = 0$ then $R/I=0$.
\item $\neg\neg \Spec(B)$
\end{enumerate}
\end{lemma}

\begin{proof}
As follows:
\begin{itemize}
\item[(i) $\Leftrightarrow$ (ii)] Omitted.
\item[(ii) $\Leftrightarrow$ (iii)] Lombardi-Quitt\'e Theorem VIII.6.1
\item[(iii) $\Leftrightarrow$ (iv)] The direct direction follows from considering $I=0$. For the converse assume $I$ f.g.\ ideal of $R$ such that $A\otimes R/I = 0$, then we have $\neg(\Spec(B)\times \Spec(R/I))$, and since $\neg\neg\Spec(B)$ we get $\neg\Spec(R/I)$.
\end{itemize}
\end{proof}


\subsection{\'Etaleness implies flatness}

\begin{lemma}
Let $X$ be a formally \'etale scheme, then $X$ is flat.
\end{lemma}

\begin{proof}
TODO
\end{proof}

\begin{theorem}\label{etale-topology-included-fppf}
Assume $S$ in the \'etale topology, then $S$ is in the fppf topology.
\end{theorem}

\begin{proof}
TODO
\end{proof}