In this section we prove the that for any f.p. algebra $A$ we have an equivalence between vector bundles over $\Spec(A)$ and f.g. projective $A$-module.

\begin{lemma}\label{localisation-hom}
Assume given a f.p. algebra $A$ and $B$ a flat $A$-algebra, with $A$-modules $M,N$ such that $M$ is finitely presented. Then we have that:
\[ \Hom_A(M,N) \otimes_AB = \Hom_B(M\otimes_AB,N\otimes_AB) \] 
\end{lemma}

\begin{proof}
Assume we have an exact sequence:
\[A^m\to A^n\to M\to 0\]
so by applying $\Hom_A(\_,N)$ we get an exact sequence:
\[0\to \Hom_A(M,N) \to N^n \to N^m\]
Then by applying $\_\otimes_AB$ to the first sequence we have an exact sequence:
\[B^m\to B^n\to M\otimes_AB\to 0\]
and then by applying $\Hom_B(\_,N\otimes_AB)$ we get an exact sequence:
\[0\to \Hom_B(M\otimes_AB,N\otimes_AB) \to (N\otimes_AB)^n \to (N\otimes_AB)^m\]
Finally using $B$ flat and applying $\_\otimes_AB$ to the second sequence, we get an exact sequence:
\[0\to \Hom_A(M,N)\otimes_AB \to N^n \otimes_AB \to N^m\otimes_AB\]
From this we can conclude.
\end{proof}

\begin{proposition}
Let $A$ be a f.p. algebra, then the equivalence:
\[\{\mathrm{bundles\ of\ f.p.\ modules\ over} \Spec(A)\} \simeq \{\mathrm{f.p.}\ A-\mathrm{modules}\}\] 
restricts to an equivalence:
\[\{\mathrm{vector\ bundles\ over} \Spec(A)\} \simeq \{\mathrm{f.p.\ projective}\ A-\mathrm{modules}\}\] 
Moreover any finitely generated projective $A$-module is in fact finitely presented.
\end{proposition}

\begin{proof}
Let $M$ be a finitely generated projective $A$-module. For any $x:\Spec(A)$, we write:
\[M_x := R\otimes_AM\]
Then we can check that for any $x:\Spec(A)$ we have that $M_x$ is projective and finitely generated, therefore $M_x$ is finite free since $R$ is local. So $x\mapsto M_x$ indeed gives a vector bundle.

Conversely let $x\mapsto M_x$ be a vector bundle over $\Spec(A)$, let us write:
\[M:= \prod_{x:\Spec(A)} M_x\]
We already know that $M$ is finitely presented. 

Since the $M_x$ are free, we know that the exists a finite cover of $\Spec(A)$ by $D(f_i)$ such that for all $i$ we have that $M_{f_i}$ is a free $A_{f_i}$-module.

Let us prove that the map of $A$-module:
\[\Hom_A(M,A^n) \to \Hom_A(M,M)\]
is surjective. To do this it is enough to prove that the induced map:
\[(\Hom_A(M,A^n))_{f_i} \to (\Hom_A(M,M))_{f_i}\]
is surjective for all $i$. But by \cref{localisation-hom} we have that this map is isomorphic to:
\[\Hom_{A_{f_i}}(M_{f_i},A_{f_i}^n) \to \Hom_{A_{f_i}}(M_{f_i},M_{f_i})\]
Since $M_{f_i}$ is a free $A_{f_i}$-module, we know that the surjection:
\[A_{f_i}^n \to M_{f_i}\]
is split, therefore the considered map is indeed surjective.

From the fact that the map:
\[\Hom_A(M,A^n) \to \Hom_A(M,M)\]
is surjective we conclude that $M$ is a direct summand of $A^n$, and therefore it is indeed projective.
\end{proof}