We have defined our interval as a qoutient of Cantor space. 
However, we have done so over an equivalence relation which we cannot compute. 
Informally speaking, we'd have to look infinitely deep in two sequences to see whether
they are equivalent, but we can only look finitely deep. 
This restricts the functions we can properly define on the interval. 
In this section, we mention two results which show this limitation. 
\begin{lemma}
  Any function from the interval to $2$ is constant. 
\end{lemma}
\begin{proof}
  Consider a function $f: 2^\mathbb N \to 2$, 
  such that whenever $x\sim y$, we have $f(x) = f(y)$. 
  By the fan theorem, there merely exists an $n$ such that 
  whenever $x =_n y$, then $f(x) = f(y)$. 
  We claim that $n$ can taken to be $0$, 
  so whenever $x =_0 y $, then $f(x) = f(y)$. 
  We will use induction on $n$. If $n=0$, $n$ can taken to be $0$. 
  Suppose that $n$ can taken to be $0$, we will show that 
  $n+1$ can also taken to be $0$. 

  Suppose that whenever $x =_{n+1} y$, we have $f(x) = f(y)$. 
  Now let $a =_n b$, we need to show that $f(a) = f(b)$. 
  If $a(n+1) = b(n+1)$, we are done. WLOG, 
  assume that $a(n+1) = 0, b(n+1) = 1$. 
  Now we know that 
  $a|_{n+1} \cdot \overline 1 \sim b_{n+1} \cdot \overline 0$, 
  and as $f$ respects $\sim$, we must therefore have 
  $f(a|_{n+1} \cdot \overline 1)  = f( b_{n+1} \cdot \overline 0)$. 
  And as $a|_{n+1} \cdot \overline 1 =_{n+1} a$, 
  and 
  $b|_{n+1} \cdot \overline o =_{n+1} b$, 
  the induction hypothesis gives us that 
  $f(a)  = f(b)$, as required. 

  By induction it follows that whenever there is some $n$ such that 
  $x=_n y$ implies $f(x) = f(y)$, we also have that 
  $x =_0 y$, implies $f(x) = f(y)$. 
  It follows that $f(x) = f(y)$ for any $x,y : 2^\mathbb N$. 
  Therefore $f$ is constant. 
\end{proof}

\begin{lemma}
  Any function from the interval to itself is continuous. 
\end{lemma}
\begin{proof}
  Let $f: 2^\mathbb N \to 2^\mathbb N$ be such that whenever 
  $x\sim y$, we have $f(x) \sim f(y)$. 
  Furthermore there exists an $n:\mathbb N$ such that whenever 
  $x =_n y$, we have $f(x) = f(y)$. 

  Let $U \subseteq I$ be a closed subset of the interval. 
\end{proof} 
